\chapter*{Acknowledgements}
Traveling back to 2022, I can still feel the confusion and uncertainty when I first attempt to explore my potential research directions and learn the rules of academia. At this moment, when finishing the thesis, I genuinely would like to express my gratitude to the people who taught me a lot and accompanied me during my Ph.D. study.

I would first like to thank my supervisor, Dr. Rui Yang, for the dedicated supervision. Throughout my studies, Dr. Yang offered great flexibility and patience when I wandered in various directions and also provided crucial suggestions many times when I encountered difficulties or fell into the wrong path. After four years of working with Dr. Yang and all the members of the Center for Intelligent Control and Optimization (CICO), I learned a lot about how to conduct academic research and how to pursue self-actualization.

I would also like to thank my supervisor Dr. Yutao Yue. As the leader of the Institute of Deep Perception Technology (IDPT), Dr. Yue provided a conducive environment for undisturbed study and research. During four years of working in IDPT, Dr. Yue taught me a lot about how academic research could empower industrial development, and the bits and pieces of daily life with members of IDPT also left an indelible mark in my memories.

I also value all my friends from all the stages before my Ph.D. study. Many of you have become my co-authors, given me valuable advice, or asked me to cite your papers during these years. Since the full name list may exceed the pages of this thesis, I would like to thank my childhood friends from Huai'an, Nanjing, my undergraduate friends now spread in Shanghai, Guangzhou, HongKong, London, Seattle, Champaign, and my postgraduate friend now live in Tokyo, Fukuoka, London.

Last and most importantly, I could never thank my parent enough for the decades of love and support mentally and financially. Although I am still waiting for the day until becoming the son of a billionaire, my parents have already taught me the most important thing by precept and example, that is to be a person with honesty, integrity and kindness, because \textit{``There is no prosthetic for an amputated spirit.''}

% and always weigh the humanity over money, 