\chapter*{Publications}
\section*{Journal paper:}
% `` and ''
\begin{enumerate}
	\item \textbf{Yuanyuan Zhang}, Runwei Guan, Lingxiao Li, Rui Yang, Yutao Yue, Eng Gee Lim, `` radarODE: An ODE-Embedded Deep Learning Model for Contactless ECG Reconstruction from Millimeter-Wave Radar'', \textit{\textbf{IEEE Transactions on Mobile Computing},} Apr. 2025.
	\item \textbf{Yuanyuan Zhang}, Rui Yang, Yutao Yue, Eng Gee Lim, ``radarODE-MTL: A Multi-Task Learning Framework with Eccentric Gradient Alignment for Robust Radar-Based ECG Reconstruction'', \textit{\textbf{IEEE Transactions on Instrumentation and Measurement},} Apr. 2025.
    \item \textbf{Yuanyuan Zhang}, Rui Yang, Yutao Yue, Eng Gee Lim, Zidong Wang, ``An Overview of Algorithms for Contactless Cardiac Feature Extraction From Radar Signals: Advances and Challenges'', \textit{\textbf{IEEE Transactions on Instrumentation and Measurement}}, Jul. 2023.
    % \item Runwei Guan, KaLok Man, Liye Jia, \textbf{Yuanyuan Zhang}, Shanliang Yao, EngGee Lim, Jeremy Smith, Yutao Yue, "Traffic Accident Scene Recognition with FMCW Radar and Vision Transformer", \textit{\textbf{International Journal of Design, Analysis and Tools for Integrated Circuits and Systems}}, Nov. 2022.
\end{enumerate}

\section*{Conference paper:}
\begin{enumerate}
	\item \textbf{Yuanyuan Zhang}, Sijie Xiong, Rui Yang, Eng Gee Lim, Yutao Yue, ``Recover from Horcrux: A Spectrogram Augmentation Method for Cardiac Feature Monitoring from Radar Signal Components'', \textit{in 2025 47th Annual International Conference of the IEEE Engineering in Medicine \& Biology Society (\textbf{EMBC2025}),} IEEE, Jul. 2025. 
\end{enumerate}

\section*{Under Review:}
\begin{enumerate}
    \item \textbf{Yuanyuan Zhang}, Haocheng Zhao, Sijie Xiong, Rui Yang, Eng Gee Lim, Yutao Yue, ``From High-SNR Radar Signal to ECG: A Transfer Learning Model with Cardio-Focusing Algorithm for Scenarios with Limited Data'', \textit{\textbf{IEEE Transactions on Mobile Computing}}. (Under Review)
    \item Sijie Xiong, \textbf{Yuanyuan Zhang}, Cheng Tang, Haoling Xiong, Yiding Li, Atsushi Shimada, ``U-MA: A Unified Framework with Differential Mamba under Parallel U-Net Scheme for Time Series Forecasting'', \textit{\textbf{Engineering Applications of Artificial Intelligence}}. (Under Review)
    \item Sijie Xiong, Cheng Tang, \textbf{Yuanyuan Zhang}, Haoling Xiong, Youhao Xu, Atsushi Shimada, ``CME-Mamba with Enhancing Nonlinear Dependencies for Time Series Forecasting'', \textit{\textbf{Applied Soft Computing}}. (Under Review)
\end{enumerate}

